conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-07-16 paper/paper.Rmd
Updated syncomat implementation example

The results are surveys that can be found in the syncomat package, which can be seen at: https://idem-lab

>>>>

One of the issues with the contact matrices generated by @prem2017 is that some countries are missing. To remedy this we generated synthetic contact matrices for 200 countries, based on a list of country names by the UN, fitted on the POLYMOD contact surveys.
We also ensured that the analysis pipeline is reproducible and transparent by utilising a targets workflow, which allows ease of editing for users.
The resulting synthetic contact matrices, and a replicable / extensible (?) analysis pipeline, can be found in the syncomat analysis pipeline ([GitHub](https://github.com/idem-lab/syncomat), [Zenodo](https://zenodo.org/records/11365943)).
